The ChEMBL database as Linked Open Data

### 2012-03-02 article.tex
Filling in more details: more used ontologies, ChEMBL 13, more authors

% For one author:
\author[A]{\fnms{Egon} \snm{Willighagen}\thanks{Huh?}}
\address[A]{Maastricht University}
\runningauthor{E.L. Willighagen et al.}

% Two or more authors:
\author[A]{\fnms{Ola} \snm{Spjuth}\thanks{}},
%\author[B]{\fnms{} \snm{}}
%\runningauthor{}
%\address[A]{}
%\address[B]{}

@@

This data set has been previously used in~\cite{} and \cite{} and some used practices have
been described in \cite{}...

@@

The ChEMBL version used in this paper is ChEMBL 12, which was released on ....

@@

Later, to satisfy the requirements for the Linked Open Drug Data \cite{Samwald2011}
network, the data was also hosted on Kasabi, a triple store hosting service
free for Open Data~\cite{}.

@@

mol:m41
      rdfs:label "CHEMBL406142" , "Bis(3-[14-Benzyl-11-(1H-indol-3-ylmethyl)-2-isobutyl-13-methyl-5-(2-methylsulfanyl-ethyl)-3,6,9,12,15,20-hexaoxo-1,4,7,10,13,16-hexaaza-bicyclo[15.2.1]icos-18-en-8-yl]-propionamide)" ;
      rdfs:subClassOf cheminf:CHEMINF_000000 ;
      cheminf:CHEMINF_000200
              m41:inchikey , m41:smiles , m41:inchi ;
      <http://www.blueobelisk.org/chemistryblogs/inchi>
              "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" ;
      <http://www.blueobelisk.org/chemistryblogs/inchikey>
              "LMCOMIDLRGMFCZ-RIPOXUOASA-N" ;
      <http://www.blueobelisk.org/chemistryblogs/smiles>
              "CC(C)C[C@@H]1N2C=CC(NC(=O)[C@H](Cc3ccccc3)N(C)C(=O)C(Cc4c[nH]c5ccccc45)NC(=O)C(CCC(=O)N)NC(=O)[C@@H](CCSCCSCC[C@H]6NC(=O)[C@H](CC(C)C)N7C=CC(NC(=O)[C@H](Cc8ccccc8)N(C)C(=O)C(Cc9c[nH]c%10ccccc9%10)NC(=O)C(CCC(=O)N)NC6=O)C7=O)NC1=O)C2=O" ;
      owl:equivalentClass <http://rdf.openmolecules.net/?InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1> , <http://bio2rdf.org/chebi:100041> , chemblid:CHEMBL406142 .
\end{verbatim}
\end{tiny}

@@

\begin{table*}
\caption{Prefixes and their matching namespaces used in this paper.} \label{namespaces}
\begin{tabular}{ll}
\hline
Common & Vocabularies \\
cito & Citation Typing Ontology~\cite{ont:cito} \\
     & http://purl.org/spar/cito/ \\

>>>>

% For one author:
\author[A]{\fnms{Egon} \snm{Willighagen}} % \thanks{Huh?}}
\address[A]{Maastricht University}
\runningauthor{E.L. Willighagen et al.}

% Two or more authors (order to be determined):
\author[B]{\fnms{Ola} \snm{Spjuth}},
\address[B]{Uppsala University}

\author[C]{\fnms{Peter} \snm{Ansell}},
\address[C]{xxx}

\author[D]{\fnms{Antony} \snm{Williams}},
\address[D]{xxx}

\author[E]{\fnms{John} \snm{Overington}},
\author[E]{\fnms{Anna} \snm{Gaulton}},
\address[E]{European Bioinformatics Institute}

%\author[B]{\fnms{} \snm{}}
%\runningauthor{}
%\address[A]{}

@@

This data set has been previously used in~\cite{Willighagen2011} ...

@@

The ChEMBL version used in this paper is ChEMBL 13, which was released on February 29 2011....

@@

Later, to satisfy the requirements for the Linked Open Drug Data \cite{Samwald2011}
network, the data was also hosted on Kasabi, a triple store hosting service
free for Open Data~\cite{kasabi}.

@@

mol:m41
      rdfs:label "CHEMBL406142" , "Bis(3-[14-Benzyl-11-(1H-indol-3-ylmethyl)-2-isobutyl-13-methyl-5-(2-methylsulfanyl-ethyl)-3,6,9,12,15,20-hexaoxo-1,4,7,10,13,16-hexaaza-bicyclo[15.2.1]icos-18-en-8-yl]-propionamide)" ;
      rdfs:subClassOf cheminf:CHEMINF_000000 ;
      cheminf:CHEMINF_000200
              m41:inchikey , m41:smiles , m41:inchi ;
      <http://www.blueobelisk.org/chemistryblogs/inchi>
              "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" ;
      owl:equivalentClass <http://rdf.openmolecules.net/?InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1> , <http://bio2rdf.org/chebi:100041> , chemblid:CHEMBL406142 .
\end{verbatim}
\end{tiny}

@@

\begin{table*}
\caption{Prefixes and their matching namespaces used in this paper.} \label{namespaces}
\begin{tabular}{ll}
\hline
Common & Vocabularies \\
cito    & Citation Typing Ontology~\cite{Shotton2010} \\
        & http://purl.org/spar/cito/ \\
cheminf & Chemical Information Ontology~\cite{Hastings2011} \\
        & http://semanticscience.org/resource/ \\
bibo    & Bibliography Ontology~\cite{Giasson2011} \\
        & http://purl.org/ontology/bibo/ \\
